Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments

### 2021-06-17 doc/paper.Rmd
added methods ref to 85% CI overlap
test out 84% CI inline code

The `dlnm` package does not currently allow modeling of factor by smooth interactions.
This means we could not include habitat as an interaction term.
We therefore fit separate models for plants in fragments and in continuous forest to allow the shape of the crossbasis function to differ between habitats.

@@

When summarizing across years and plots, the proportion of *Heliconia acuminata* that survived in CF and 1-ha was similarly high ($P_{surv} = 0.95$; Figure \@ref(fig:eda)b).
The proportion of surviving plants was lowest in the 2003--2004 transition year ($P_{surv} = 0.92$), which coincided with droughts in both the 2003 and 2004 rainy seasons (Figure \@ref(fig:eda)b,d) and was preceded by a drop in average plant size in the 2002--2003 transition year (Figure \@ref(fig:eda)a).
The lowest survival for 1-ha fragment plots ($P_{surv} = 0.93$) was for the 2005--2006 transition year, which encompassed a moderate drought in October 2005 and and wetter than average conditions (SPEI \> 0.5) in December 2005 and January 2006 (Figure \@ref(fig:eda)b,d).
Survival was size dependent in both continuous forest and 1-ha fragments ($p < 0.001$ for the effect of log-transformed plant size in year t on survival in year t+1 in both habitats).
While the survival probability of large plants approached 1 in both habitat types (Figure \@ref(fig:size-plot)b), the survival of the smallest plants was higher in 1-ha fragments.
However, the 95% confidence intervals for 1-ha fragments and continuous forest overlapped for all sizes.

>>>>

The `dlnm` package does not currently allow modeling of factor by smooth interactions.
This means we could not include habitat as an interaction term.
We therefore fit separate models for plants in fragments and in continuous forest to allow the shape of the crossbasis function to differ between habitats.
Significant main effects of habitat type were assessed by looking for overlap in the 84% confidence intervals of model intercepts (84% CIs of two samples drawn from the same population overlap about 95% of the time [@paytonOverlappingConfidenceIntervals2003]).

@@

The proportion of surviving plants was lowest in the 2003--2004 transition year ($P_{surv} = 0.92$), which coincided with droughts in both the 2003 and 2004 rainy seasons (Figure \@ref(fig:eda)b,d) and was preceded by a drop in average plant size in the 2002--2003 transition year (Figure \@ref(fig:eda)a).
The lowest survival for 1-ha fragment plots ($P_{surv} = 0.93$) was for the 2005--2006 transition year, which encompassed a moderate drought in October 2005 and and wetter than average conditions (SPEI \> 0.5) in December 2005 and January 2006 (Figure \@ref(fig:eda)b,d).
Survival probability did not differ significantly between continuous forest and 1 ha fragments (estimate and 84% CI were `r pull_ci(tar_read(s_cf))` , and `r pull_ci(tar_read(s_1ha))` for continuous forest and 1 ha fragments, respectively).
Survival was size dependent in both continuous forest and 1-ha fragments ($p < 0.001$ for the effect of log-transformed plant size in year t on survival in year t+1 in both habitats).
While the survival probability of large plants approached 1 in both habitat types (Figure \@ref(fig:size-plot)b), the survival of the smallest plants was higher in 1-ha fragments.
However, the 95% confidence intervals for 1-ha fragments and continuous forest overlapped for all sizes.
